---
title: "Development Economics I - Project 2"
author: "Sepehr Hasanvand"
date: "`r Sys.Date()`"
output:
    html_document:
        theme: readable    
        highlight: kate
        toc: true    
        toc_depth: 4
        toc_float: true    
        df_print: paged
        code_folding: hide    
        css: styles.css
editor_options:
  markdown:
    wrap: 72
---

```{r setup, include=FALSE, message=FALSE}
knitr::opts_chunk$set(echo = TRUE)
knitr::opts_chunk$set(warning = FALSE)
knitr::opts_chunk$set(cache = TRUE)
```

Required libraries

```{r, results='asis',message=FALSE}
library(readxl)
library(dplyr)
library(purrr)
library(ggplot2)
library(stargazer)
library(tidyverse)
library(RODBC)
library(tibble)
library(knitr)
library(ineq)

library(shiny)
library(leaflet)
library(sf)
```

Importing HEIS data:
```{r}
db <- odbcDriverConnect("Driver={Microsoft Access Driver (*.mdb, *.accdb)};
                        DBQ=D:/Masters student/Term 3/Dev/Project 2/Data/raw data1401_2/raw data1401/HB1401_14020611.mdb")
#Importing tables
# List of suffixes for the table names
suffixes_data <- c("Data", "P1", "P2")
suffixes_expenditure <- paste0("P3S", c("01", "02", "03", "04", "05", "06", "07", "08", "09", "11", "12"))
suffixes_income <- paste0("P4S", c("01", "02", "03", "04"))

# Function to load data into a tibble
load_data <- function(table_name) {
  as_tibble(sqlFetch(db, table_name, rownames = TRUE))
}

# Load the data for rural and urban datasets
for (suffix in c(suffixes_data, suffixes_expenditure, suffixes_income)) {
  assign(paste0("R1401", suffix), load_data(paste0("R1401", suffix)))
  assign(paste0("U1401", suffix), load_data(paste0("U1401", suffix)))
}


```
Data Cleaning
```{r}
# Combining urban and rural data
suffixes <- c(
  "Data", "P1", "P2", "P3S01", "P3S02", "P3S03", "P3S04", "P3S05", "P3S06", "P3S07", "P3S08", 
  "P3S09", "P3S11", "P3S12", "P4S01", "P4S02", "P4S03", "P4S04"
)

# Loop to create and merge tables
for (suffix in suffixes) {
  # Create table names for R, U, and T
  R_name <- paste0("R1401", suffix)
  U_name <- paste0("U1401", suffix)
  T_name <- paste0("T1401", suffix)
  # Merge tables and store the result in T
  assign(T_name, rbind(get(R_name), get(U_name)))
}
# Removing extra data frames
rm(list = ls(pattern = "^[RU]1401"))

# Dropping and merging
T1401Data <- T1401Data %>%
  select(Address,weight)
T1401Data <- merge(T1401Data, T1401P1, by = "Address", all = TRUE)

# making Province variable and renaming
T1401Data <- T1401Data %>% 
   mutate(Province = substr(Address, 2, 3),
          Urban=substr(Address,1,1)) %>% 
  rename(Radif=DYCOL01,
         Nesbat=DYCOL03,
         Gender=DYCOL04,
         Age=DYCOL05,
         Savad=DYCOL06,
         Tahsil=DYCOL07,
         Madrak=DYCOL08,
         Faaliat=DYCOL09,
         Marriage=DYCOL10)
  T1401P1 <- T1401P1 %>% 
    select(Address,DYCOL03) %>% 
    rename(Nesbat=DYCOL03)

# Map province codes to province names
Province <- c(Markazi = "00", Ardabil = "24", Bushehr = "18", `Chaharmahal and Bakhtiari` = "14",
  `East Azerbaijan` = "03", Fars = "07", Gilan = "01", Golestan = "27",
  Hamadan = "13", Hormozgan = "22", Ilam = "16", Isfahan = "10",
  Kerman = "08", Kermanshah = "05", Khuzestan = "06", `Kohgiluyeh and Boyer-Ahmad` = "17",
  Kurdistan = "12", Lorestan = "15", Alborz = "30", Mazandaran = "02",
  `North Khorasan` = "28", Qazvin = "26", Qom = "25", `Razavi Khorasan` = "09",
  Semnan = "20", `Sistan and Baluchestan` = "11", `South Khorasan` = "29", Tehran = "23",
  `West Azerbaijan` = "04", Yazd = "21", Zanjan = "19")

# Correct the code to map the "province" from "Address"
T1401Data <- T1401Data %>% 
  mutate(province = fct_recode(as.factor(substr(Address, 2, 3)), !!!Province))

# View the modified data frame (optional)
  
  
  
T1401P3S01 <- merge(T1401Data, T1401P3S01, by = "Address", all = TRUE)



# Labeling Values
T1401P3S01 <- T1401P3S01 %>% 
  rename(Code_Kala = DYCOL01,
         Tahie = DYCOL02,
         Meghdar_G = DYCOL03,
         Meghdar_KG = DYCOL04,
         Price = DYCOL05,
         Arzesh = DYCOL06) %>%
  mutate(Code_Kala = as.character(Code_Kala), 
         Code_Kala = case_when(
           Code_Kala %in% c("11141", "11142", "11143", "11144") ~ "Nan",
           Code_Kala %in% c("11111", "11112", "11113", "11114", "11115", 
                            "11116", "11117", "11118") ~ "Bereng",
           Code_Kala == "11164" ~ "Macaroni",
           Code_Kala == "11731" ~ "SibZamini",
           Code_Kala %in% c("11211", "11212", "11213") ~ "Goosht_GH",
           Code_Kala %in% c("11231", "11232") ~ "Goosht_Sefid",
           Code_Kala == "11768" ~ "Adas",
           Code_Kala %in% c("11411", "11412") ~ "Shir",
           Code_Kala %in% c("11425", "11426") ~ "Mast",
           Code_Kala %in% c("11441", "11442") ~ "Tokhm_Morgh",
           Code_Kala %in% c("11428", "11429") ~ "Panir",
           Code_Kala %in% c("11611", "11612", "11613", "11614", "11615", 
                            "11616", "11617", "11618", "11619", 
                            "11621", "11622", "11623", "11624", "11625", 
                            "11631", "11632", "11633", "11634", "11635", 
                            "11641", "11642", "11643") ~ "Miveh",
           Code_Kala %in% c("11711", "11712", "11713", "11714", "11715") ~ "Sabzi_Barg_Sabz",
           Code_Kala %in% c("11741", "11742", "11735") ~ "Digar_Sabzi_ha",
           Code_Kala == "11812" ~ "Shekar",
           Code_Kala == "11533" ~ "Roghan",
           TRUE ~ Code_Kala 
         )) %>%
  mutate(i_weight = case_when(
    Nesbat == 1 ~ 1,
    Age > 18 & Nesbat != 1 ~ 0.8,
    Age <= 18 & Nesbat != 1 ~ 0.5
  ))

# تبدیل NA به صفر
T1401P3S01 <- T1401P3S01 %>%
  mutate(
    Meghdar_G = if_else(is.na(Meghdar_G), 0, Meghdar_G),
    Meghdar_KG = if_else(is.na(Meghdar_KG), 0, Meghdar_KG)
  ) %>%
  # تبدیل گرم به کیلوگرم و جمع کردن مقادیر
  mutate(Meghdar_KG = Meghdar_KG + Meghdar_G / 1000)


# Create a lookup vector (data frame) mapping Code_Kala to the corresponding needs_kg values
needs_lookup <- tibble(
  Code_Kala = c("Nan", "Bereng", "Macaroni", "SibZamini", "Adas", "Shir", "Mast",
                "Goosht_GH", "Goosht_Sefid", "Tokhm_Morgh", "Panir", "Miveh",
                "Sabzi_Barg_Sabz", "Digar_Sabzi_ha", "Roghan", "Shekar"),
  needs_kg = c(8, 3, 0.7, 1.5, 0.6, 7, 3, 1.2, 1.5, 0.7, 0.45, 9, 9, 4.5, 0.9, 1)
)

# Process the data frame and create new variables
price <- T1401P3S01 %>%
  group_by(Code_Kala) %>%
  mutate(
    price_index = sum(Arzesh * i_weight, na.rm = TRUE) / 
                  sum(Meghdar_KG * i_weight, na.rm = TRUE)
  ) %>%
  mutate(price_index = if_else(is.nan(price_index) | is.infinite(price_index), NA_real_, price_index)) %>%
  ungroup()%>%
  select(Address, Code_Kala, Province, price_index,Urban,weight) %>%
  filter(!is.na(as.numeric(Code_Kala)) == FALSE) %>%
  left_join(needs_lookup, by = "Code_Kala") %>% 
  mutate(Arzesh_Kala=price_index * needs_kg*weight)

Poverty_line <- price %>%
  group_by(Code_Kala, Urban) %>% 
  summarize(mean_Arzesh = mean(Arzesh_Kala, na.rm = TRUE), .groups = "drop") %>% 
    ungroup()%>%
  group_by(Urban) %>% 
  summarize(Poverty_line = mean(mean_Arzesh, na.rm = TRUE), .groups = "drop")


kable(Poverty_line, 
      format = "html",
      caption = "Poverty line")

```
Part II:
Inequality

2.1:
```{r}
Welfare <- read.csv("D:/Masters student/Term 3/Dev/Project 2/Data/nemone_2_darsadi_1402/nemone_2_darsadi_1402.csv")
```

```{r}
Welfare <- Welfare %>%
  mutate(proxy = CardPerMonth_1402*12 + Daramad)

gini=Gini(Welfare$proxy)

cat("Gini Coefficient using welfare data:", gini, "\n")
```


```{r}
Income <- T1401P4S01 %>% 
  select(Address, DYCOL15) %>% 
  rename(Mozd=DYCOL15)

Income <- Income %>%
  left_join(T1401P4S02 %>% select(Address, DYCOL15), by = "Address") %>% 
  rename(Azad=DYCOL15) %>% 
    left_join(T1401P4S03 %>% select(-DYCOL01), by = "Address") %>% 
    mutate(Mothefareghe= DYCOL03+DYCOL04+DYCOL05+DYCOL06+DYCOL07+DYCOL08) %>% 
  select(Address,Mozd,Azad,Mothefareghe) %>% 
        left_join(T1401P4S04 %>% select(Address,Dycol05), by = "Address") %>% 
  rename(other=Dycol05) %>% 
      left_join(T1401Data %>% select(Address), by = "Address") %>% 
  mutate(Income=Mozd+Azad+Mothefareghe+other) %>% 
      left_join(T1401Data %>% select(Address,province), by = "Address")

gini_HEIS=Gini(Income$Income)

cat("Gini Coefficient using HEIS data:", gini_HEIS, "\n")
```
Top 1% Share of Income of HEIS data
```{r}
top_1_percent <- Income %>%
  arrange(desc(Income)) %>% 
  slice_head(prop = 0.01) %>%   # انتخاب یک درصد بالای داده‌ها
  summarise(sum_top_1_percent = sum(Income, na.rm = TRUE))

# محاسبه مجموع کل Income
total_income <- sum(Income$Income, na.rm = TRUE)

# محاسبه نسبت
ratio <- top_1_percent$sum_top_1_percent / total_income

# نمایش نتیجه
print(paste("Ratio of top 1% income to total income:", ratio))
```
```{r}
top_1_percent_welfare <- Welfare %>% 
  arrange(desc(proxy)) %>% 
  slice_head(prop = 0.01) %>%   # انتخاب یک درصد بالای داده‌ها
  summarise(sum_top_1_percent_w= sum(proxy, na.rm = TRUE))

# محاسبه مجموع کل Income
total_income_Welfare <- sum(Welfare$proxy, na.rm = TRUE)

# محاسبه نسبت
ratio_welfare <- top_1_percent_welfare$sum_top_1_percent_w / total_income_Welfare

# نمایش نتیجه
print(paste("Ratio of top 1% income to total income of Welfare Data:", ratio_welfare))
  
```

2.2:

Since we have used a proxy for income in the welfare data but actual income in the HEIS data, the income values for individuals differ between the two datasets. Additionally, the samples in these two datasets are different, meaning that we do not have a common sample from the population. As a result, the Gini coefficient and the top 1% income share may differ between the two datasets.

################################################
Part III:
Calculating gini coefficient for all of the provinces in Welfare Data
```{r}
compute_gini <- function(x) {
  return(Gini(x))  
}

gini_by_province_Welfare <- Welfare %>%
  group_by(SabteAhval_provincename) %>%
  summarise(gini_coefficient = compute_gini(proxy), .groups = "drop") %>% 
  rename(province_farsi=SabteAhval_provincename)

print(gini_by_province_Welfare)
```
Calculating gini coefficient for all of the provinces in Heis Data
```{r}
compute_gini <- function(x) {
  return(Gini(x))
}


gini_by_province <- Income %>%
  group_by(province) %>%
  summarise(gini_coefficient = compute_gini(Income), .groups = "drop")

print(gini_by_province)
```


```{r warning=FALSE}
provinces_map <- st_read("C:/Users/sepehr/Downloads/Mapping/Mapping/iranmap/irn_admbnda_adm1_unhcr_20190514.shp")
provinces_map <- provinces_map %>% 
  rename(province=ADM1_EN)

provinces_map_HEIS <- merge(provinces_map, gini_by_province, by = "province")

ggplot(data = provinces_map_HEIS) +
  geom_sf(aes(fill = gini_coefficient)) +  
  scale_fill_viridis_c(option = "C") +
  theme_minimal() +
  labs(title = "Map of Iran", fill = "Gini Coeffient by HEIS Data")
```
```{r}
gini_by_province_Welfare <- gini_by_province_Welfare[-1, ]
 provinces_map <- provinces_map %>% 
  rename(province_farsi=ADM1_FA)

provinces_map_welfare <- merge(provinces_map, gini_by_province_Welfare, by = "province_farsi")


ggplot(data = provinces_map_welfare) +
  geom_sf(aes(fill = gini_coefficient)) +  
  scale_fill_viridis_c(option = "C") +
  theme_minimal() +
  labs(title = "Map of Iran", fill = "Gini Coeffient by Welfare Data")
```

